Dish: Distribution-oblivious Shell Scripting

### 2020-02-18 pldi/draft.tex
New intro sketch for OSDI

%% Title information
\title{Dish: Distribution-oblivious Shell Scripting}         %% [Short Title] is optional;
% \titlenote{with title note}             %% \titlenote is optional;
%                                         %% can be repeated if necessary;
%                                         %% contents suppressed with 'anonymous'
% \subtitle{Subtitle}                     %% \subtitle is optional
% \subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

>>>>

%% Title information
\title{Dish: Distribution-oblivious Shell Scripting}         %% [Short Title] is optional;
%% \title{Extensible data processing in the shell}

% \titlenote{with title note}             %% \titlenote is optional;
%                                         %% can be repeated if necessary;
%                                         %% contents suppressed with 'anonymous'
% \subtitle{Subtitle}                     %% \subtitle is optional
% \subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

\kk{New intro sketch:}

\kk{Note: A point that we need to establish and convince the readers
  about is that the Shell IS used already for data-processing, and
  that we are not just proposing it as an alternative to other
  systems. We do not propose migrating to shell scripts if you already
  have a parallel/efficient solution. I am not sure if that needs a
  specific paragraph of its own at the start of the
  introduction. Like: ``Consider the following bash script that does
  some simple data processing... Examples like that exists in several
  domains/applications (examples, cite).''}

\begin{itemize}
\item Why is parallelism important (especially in the context of data
  processing). Significant performance benefits as most computer
  systems today have multiple processors that are under utilized
\item (Similarly to how it is now) unfortunately, it is quite hard
  reaping these benefits in contrast to sequential data
  processing. [Show Bash pipeline].
\item To benefit from parallelism, the current options are
  extreme. Either very fine-grained and low level (parallelism using
  fine-grained C libraries) for maximum performance, or very coarse
  grained and bulky where one has to use a proper big-data framework.
\item The common thing is that one needs to rewrite big part of their
  application, often requiring expertise and redesigning its
  architecture, in order to get benefits that in the end might not
  explain the cost.
\item To address this issue, we propose Dish, a thin layer that
  automatically! parallelizes a given shell script. Key insight is
  that a large subset of the shell language can be encoded in a
  dataflow graph model, a flexible representation that allows for
  parallelization optimizations.
\item Study of the shell primitives, identification of
  families/classes of commands that share
  distributability/parallelization properties, and a classification of
  coreutils/POSIX commands in these distributability properties.
\item Dataflow graph model that is suitable for the shell
\item A set of optimizations on this model that can be thought of as
  rewriting rules on the dataflow graph, that are sound and exploit
  parallelism.
\end{itemize}

\kk{End of new intro sketch}
